Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-06-20 sports_analytics.Rmd
some notes on wp in basketball and other sports

@Stern1994 brownian

@Deshpande2016 bayesian

@McFarlane2019 nba logistic

@@

https://arxiv.org/pdf/2204.11777.pdf

@Brenzel2019 curling markov

@Maymin2020 esport!

@Guan2022 wp for rugby

>>>>

@Stern1994 used Brownian motion to investigate the scoring process of basketball. The model introduced by @Stern1994 is a probit regression model, which provides an estimate for the probability of winning for a home team, taking into account the score difference between the teams and the current game time.

@Deshpande2016 extended @Stern1994's framework by applying it in a Bayesian setting.

@McFarlane2019 used logistic regression to estimate win probability for evaluating end-of-game decisions in the NBA

@@

Examples of win probability can also be found in other sports, with a diverse range of statistical techniques being used to estimate the probability of winning for a player or team.

@Brenzel2019 used a three-dimensional Markov model to estimate win probability in curling.

In esport, @Maymin2020 proposed a well-calibrated in-game win probability model for each specific moment during a game of League of Legends.

More recently, @Guan2022 developed an in-game win probability model for the National Rugby League using a functional data analysis approach.
